---
title: "Investigation of Exponential Distribution in R and Comparison with Central Limit Theorem"
author: "khsarma"
date: "July 3, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Overview
In this project, we are going to simulate Exponential distribution in R and analyse below points:
1. Show the sample mean and compare it to the theoretical mean of the distribution.
2. Show how variable the sample is (via variance) and compare it to the theoretical variance of the distribution.
3. Show that the distribution is approximately normal.

### Simulations
For simulation purpose, we are going to assume few details:
1. Rate parameter lambda is set as 0.2
2. Consider 40 exponentials
3. Consider number of simulations as 1000
```{r}
set.seed(7)
lambda <- 0.2
noSim <- 1000
noExp <- 40
```

### Sample Mean versus Theoretical Mean
#### Theoretical Mean
Theoretical Mean is considered as 1/lambda
```{r}
theoryMean <- 1/lambda
theoryMean
```

#### Sample Mean
Generating 1000 simulations of 40 exponentials:
```{r}
expMat <- matrix(rexp(noExp*noSim, lambda), noSim)
dim(expMat)
```
Calculating Sample mean
```{r}
expMatMean <- apply(expMat, 1, mean)
expMean <- mean(expMatMean)
```
Hence, Sample mean `r round(expMean,3)` is approximately equal to Theoretical mean `r round(theoryMean,3)`.

### Sample Variance versus Theoretical Variance
#### Theoretical Variance
Theoretical Variance is considered as (1/lambda)^2/(n)
```{r}
theoryVar <- (1/lambda)^2/(noExp)
theoryVar
```

#### Sample Variance
Calculating Sample variance
```{r}
expVar <- var(expMatMean)
```
Hence, Sample variance `r round(expVar,3)` is approximately equal to Theoretical variance `r round(theoryVar,3)`.

### Distribution of averages of 40 Random Exponential variables
Let us create a density histogram of the averages of 40 Random variables that we simulated.
``` {r, include = FALSE, results = FALSE}
library(ggplot2)
```
```{r}
ggplot(data.frame(x = expMatMean), aes(x = x)) +
  geom_histogram(aes(y = ..density..), 
                binwidth = 0.2, fill = "steelblue", color = "white") +
  stat_function(fun = dnorm, color = 'black',
                args = list(mean = expMean, 
                                     sd = sqrt(theoryVar))) + 
  geom_vline(xintercept = expMean, size = 1) + 
  xlab("Means") + 
  ylab("Density") + 
  ggtitle("Distribution of Averages of 1000 samples of 40 Random Exponential variables")
```

From the graph it can be observed that the distribution is approximately normal.