---
title: "Inferential Analysis of ToothGrowth data set"
author: "khsarma"
date: "July 4, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Overview
#### 1a Load ToothGrowth Data set
``` {r, include = FALSE, results = FALSE}
library(ggplot2)
library(dplyr)
```
Load ToothGrowth data set from datasets library
```{r}
library(datasets)
data(ToothGrowth)
```

#### 1b Exploring Data set
Let's check the structure of the data set.
```{r}
str(ToothGrowth)
```
At supp factor level, let's check the count of obervations against dose variable.
```{r}
table(ToothGrowth$supp, ToothGrowth$dose)
```

#### 2 Summary of Data
Summaries of the three variables.
```{r}
summary(ToothGrowth)
```

Using box plot, check the association of len with dose
```{r}
ggplot(ToothGrowth, aes(x = factor(dose), y = len, fill = factor(dose))) +
  geom_boxplot()
```

From the graph, it can be observed that with increase in dosage length increases.
Using box plot, check the association of len with supp
```{r}
ggplot(ToothGrowth, aes(x = supp, y = len, fill = supp)) +
  geom_boxplot()
```

From the graph, it can be observed that Orange Juice helped in more length when compared to Vitamin C supplement.
Using bar graph, check the association of len with supp and dose together
```{r}
ggplot(ToothGrowth, aes(x=factor(dose), y=len, fill=supp)) + geom_bar(stat='identity', position='dodge')
```

From the graph, it can be observed that Orange juice contributed to more increase in length for 0.5 and 1.0 dosages. And Vitamin C supplement contributed to more increase in length for 2.0 dosage.

#### 3 Comparison of Tooth growth by Supp and Dose
```{r}
t.test(ToothGrowth$len, ToothGrowth$dose, paired = F, var.equal = F)
```
```{r}
t.test(ToothGrowth$len, ToothGrowth$dose, paired = F, var.equal = F)
```

#### 4 Conclusions and Assumptions
##### 4a Assumptions
##### 4b Conclusions